Software Architectures to Integrate Workflow Engines in Science Gateways

### 2016-04-26 paper.tex
Merge remote-tracking branch 'glatard/master'
# Conflicts:
#	paper.tex fixed
Closed note based on discussion in #7.

\paragraph{Robustness} No component is specific to workflow execution
(\texttt{R$_1$}=0), and only interaction \texttt{e} is
(\texttt{R$_2$}=1)\answerednote{sorina}{I understand why this is 1 (and why
  interactions c and b are not counted here), but I wonder whether we
  can simply ignore these interactions because they are not specific
  to workflow execution. As far as robustness is concerned, the
  transfers have to be successful anyway...}{Tristan}{We cannot just
  ignore these interactions in the architecture because they are
  required for the system to work. The transfers have to be successful
  but data movements in the workflow will use the same code as data
  movements done in the science gateway, which will make this
  architecture more robust than service for instance. In VIP, for
  instance, the code used in the GASW wrapper to transfer data (c2) is
  completely independent from the ``file transfer'' module in the
  platform (c1), which is detrimental to robustness}.

>>>>

\paragraph{Robustness} No component is specific to workflow execution
(\texttt{R$_1$}=0), and only interaction \texttt{e} is
(\texttt{R$_2$}=1)\closedanswerednote{sorina}{I understand why this is 1
  (and why interactions c and b are not counted here), but I wonder
  whether we can simply ignore these interactions because they are not
  specific to workflow execution. As far as robustness is concerned,
  the transfers have to be successful anyway...}{Tristan}{We cannot
  just ignore these interactions in the architecture because they are
  required for the system to work. The transfers have to be successful
  but data movements in the workflow will use the same code as data
  movements done in the science gateway, which will make this
  architecture more robust than service for instance. In VIP, for
  instance, the code used in the GASW wrapper to transfer data (c2) is
  completely independent from the ``file transfer'' module in the
  platform (c1), which is detrimental to robustness}{Tristan}{Closed,
  see github issue \#7.}.
